Julkaisutoiminta Vaasassa 1764-1917

### 2015-03-22 inst/examples/Vaasa.Rmd
Vaasa, osa 7

```{r, echo=FALSE, fig.width=20, fig.height=10}
par(las=1)
par(mgp=c(7,2,0))
par(mar=c(8,13,5,3))
plot(vaasa$published_in,vaasa$n,pch="|",cex.main=3.2,main="Julkaisutoiminta Vaasassa 1764-1917",cex.lab=3.2,xlab="",ylab="Dokumenttia / vuosi",axes=FALSE,col="black")
lines(vaasa$published_in,vaasa$m,type="l",lty=3,col="black",lwd=4)
axis(side = 1, at = c(1764,1809,1863,1917),cex.axis=3.2)
axis(side = 2, at = c(0,40,80,120,160,194),cex.axis=3.2)
```

```{r, echo=FALSE, fig.width=20, fig.height=10}
par(las=1)
par(mgp=c(7,2,0))
par(mar=c(8,13,5,3))
plot(vaasa$published_in,vaasa$n,pch="|",cex.main=3.2,main="Julkaisutoiminta Vaasassa 1764-1917",cex.lab=3.2,xlab="",ylab="Dokumenttia / vuosi",axes=FALSE,col="black")
lines(vaasa$published_in,vaasa$m,type="l",lty=3,col="black",lwd=4)
axis(side = 1, at = c(1764,1780,1800,1820,1840,1860,1880,1900,1917),cex.axis=3.2)
axis(side = 2, at = c(0,40,80,120,160,194),cex.axis=3.2)
```

>>>>

```{r, echo=FALSE, fig.width=20, fig.height=10}
par(las=1)
par(mgp=c(10,3,0))
par(mar=c(7,17,6,4))
plot(vaasa$published_in,vaasa$n,cex=1.8,pch="|",cex.main=5.0,main="Julkaisutoiminta Vaasassa 1764-1917",cex.lab=5.0,xlab="",ylab="Dokumenttia / vuosi",axes=FALSE,col="black")
lines(vaasa$published_in,vaasa$m,type="l",lty=3,col="black",lwd=4)
axis(side = 1, at = c(1764,1809,1863,1917),cex.axis=3.2)
axis(side = 2, at = c(0,40,80,120,160,194),cex.axis=3.2)
```

```{r, echo=FALSE, fig.width=20, fig.height=10}
par(las=1)
par(mgp=c(10,3,0))
par(mar=c(7,17,6,4))
plot(vaasa$published_in,vaasa$n,cex=1.8,pch="|",cex.main=5.0,main="Julkaisutoiminta Vaasassa 1764-1917",cex.lab=5.0,xlab="",ylab="Dokumenttia / vuosi",axes=FALSE,col="black")
lines(vaasa$published_in,vaasa$m,type="l",lty=3,col="black",lwd=4)
axis(side = 1, at = c(1764,1800,1840,1880,1917),cex.axis=3.2)
axis(side = 2, at = c(0,40,80,120,160,194),cex.axis=3.2)
```
